---
title: "Essay The Model"
author: "Gergel Anastasia"
date: "12/14/2018"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, message=FALSE, warning=FALSE)
```

```{r}
library(stargazer)
library(dplyr)
```

Please cite as: 

 Hlavac, Marek (2018). stargazer: Well-Formatted Regression and Summary Statistics Tables.
 R package version 5.2.2. https://CRAN.R-project.org/package=stargazer 


Too many NA's in `v2mecenefi` and `v2mecenefibin` -- internet censorship and internet binary. 
```{r}
setwd("/Users/herrhellana/Dropbox/_Maths&Data analysis/Stats 3 year/Home assignments/Essay")
data <- read.csv("FinalDATA.csv")
summary(data)
# stargazer(data)




# ------------------------- #
# Remove duplicates
# ------------------------- #

sub <- cbind(as.character(data$COWc), data$year)
which(duplicated(sub))  # print duplicates. That's Russia, YUG and some others. Obviously

library(plm)
data <- data[-which(duplicated(sub)), ] # remove duplicates from the dataset
FinalData <- pdata.frame(data, index = c("COWc", "year"), # declare a PD
                         row.names = TRUE)

#################### WARNING: ####################
# DO NOT EVER LOAD PLM PACKAGE BEFORE THIS TRANSFORMATION
# cause otherwise it would mess with the lag function 
# (plm and dplyr are not compatible)

detach("package:plm", unload=TRUE)

# create a lagged repression variable
# create a new database with lagged variables 
data <- data %>% group_by(COWc) %>% 
  mutate(LAGlatent = lag(latentmean, n=1),
         LAG2latent = lag(latentmean, n=2),
         LAGgrowth = lag(gdppc_growth, n=1),
         LAG3growth = lag(gdppc_growth, n=3), 
         LAGriots = lag(cnts_domestic6, n=1),
         LAGprotests = lag(cnts_domestic8, n=1),
         LAGmedia = lag(v2mecenefm, n=1))

write.csv(file = "/Users/herrhellana/Documents/_Maths&Data analysis/Stats 3 year/Home assignments/Essay/FinalDataLatent.csv", x = data)
```


NA's for GDP per capita (length = 46) in ALG (1962-69), KUW (1961-73), QAT (1971-73), UAE (1973-84). 
`e_Civil_War` is a better control variable (less NA's). 

# ---------------------------------------------------- #
# -------------------- Visualization ----------------- #
# ---------------------------------------------------- #
Repressions density: 
```{r}
library(ggplot2)

ggplot(data, aes(x=latentmean))+
  geom_density(color="tomato4", fill="tomato", alpha=0.4) +
  xlab("repression variable values") + 
  theme(axis.title = element_text(size=9, hjust=0.4)) +
  ggtitle("Repressions worlwide density, 1960-2013") +
  theme(plot.title = element_text(size=10)) 

# autocracies
ggplot(data[which(data$v2x_polyarchy <= 0.5), ], aes(x=latentmean))+
  geom_density(color="tomato4", fill="tomato", alpha=0.4) +
  xlab("repression variable values") + 
  theme(axis.title = element_text(size=9, hjust=0.4)) +
  ggtitle("Repressions density in Autocracies, 1960-2013") +
  theme(plot.title = element_text(size=10)) 

# democracies
ggplot(data[which(data$v2x_polyarchy >= 0.5), ], aes(x=latentmean))+
  geom_density(color="lightblue1", fill="lightblue", alpha=0.4) +
  xlab("repression variable values") + 
  theme(axis.title = element_text(size=9, hjust=0.4)) +
  ggtitle("Repressions density in Democracies, 1960-2013") +
  theme(plot.title = element_text(size=10)) 



# negative econ growth
ggplot(data[which(data$gdppc_growth >= 0.5), ], aes(x=latentmean))+
  geom_density(color="lightblue1", fill="lightblue", alpha=0.4) +
  xlab("repression variable values") + 
  theme(axis.title = element_text(size=9, hjust=0.4)) +
  ggtitle("Repressions density in Democracies, 1960-2013") +
  theme(plot.title = element_text(size=10)) 
```

Create a subset to work with. 

```{r}
# subset with variables needed
subset <- data %>% select("COWc", "year", "latentmean", "latentsd", 
                          "LAGlatent", "LAG2latent", "gdppc_growth", "LAGgrowth", "LAG3growth", "cnts_domestic6", "LAGriots", "cnts_domestic8", "LAGprotests", 
                          "v2mecenefm", "LAGmedia", "v2x_polyarchy", "v2x_corr", "v2mecrit", "logGDPpc", "logPOP") 


subset <- na.omit(subset)
# we've left with 82% of observations
nrow(subset)/(161*53)
```


# ---------------------------------------------------- #
# ----------------------- MODEL ---------------------- #
# ---------------------------------------------------- #

Simple models. 
```{r}
# library(plm)
library(pcse)
library(foreign)


# first, specify the model without a within-group transformation, use lm function
ols <- lm(latentmean ~ gdppc_growth + cnts_domestic6 + v2x_polyarchy + v2mecenefm + v2x_corr + logPOP + logGDPpc, data = subset)
summary(ols)
```



# ---------------------------------------------------- #
# ------------------ DYNAMIC MODELS ------------------ #
# ---------------------------------------------------- #

From CNTS: 
General Strikes (`domestic2`).
Guerrilla Warfare (`domestic3`).
Riots (`domestic6`).
Revolutions (`domestic7`).
Anti-government Demonstrations (`domestic8`).

```{r}
#################################
       # Bunch of tests
#################################

# first, specify the model without a within-group transformation, use lm function
ols <- lm(latentmean ~ gdppc_growth, data = subset)
summary(ols)
# second, use pcse
pcse <- pcse(ols, groupN = ols$country, groupT = ols$time)
summary(pcse)

#################
# Within model (estimate by using "plm")
model0 <- plm(latentmean ~ gdppc_growth + logPOP + logGDPpc, effect = "twoways", data = subset, index=c("COWc", "year"), model="within")
summary(model0, vcov = vcovBK) # Beck-Katz panel-corrected errors

model1 <- plm(latentmean ~ gdppc_growth + v2mecenefm + cnts_domestic6 + v2x_polyarchy + logPOP + logGDPpc, effect = "twoways", data = subset, index=c("COWc", "year"), model="within")
summary(model1, vcov = vcovBK)

model2 <- plm(latentmean ~ gdppc_growth*v2x_polyarchy + v2mecenefm + cnts_domestic6 + logPOP + logGDPpc, effect = "twoways", data = subset, index=c("COWc", "year"), model="within")
summary(model2, vcov = vcovBK)
stargazer(model0, model1, model2)

ols <- plm(latentmean ~ gdppc_growth + v2mecenefm + cnts_domestic6 + v2x_polyarchy + logPOP + logGDPpc, data=subset, index=c("COWc", "year"), model="pooling")
summary(ols)
pFtest(model0, ols) # significant effects


# test for serial correlation 
pdwtest(model0, alternative = "two.sided") # Durbin-Watson (AR1)
pbgtest(model1, order = 1) # Breusch-Godfrey 



# define the dependence with ACF and PACF
residuals <- model2$residuals
acf(residuals) # correlogram suggest to include lots of lags
# pacf(res)
# VERY SIGNIFICANT LAGS
# acf is about variance. pcf -- about moving average. 



####################################################
#                 DYNAMIC MODELS
####################################################
library(dyn)
# controls (logPOP, logGDPpc)
# advanced controls (v2mecenefm, v2x_corr)
LDV2_residuals <- ldv_lag2$residuals

ldv_lag2 <- dyn$lm(latentmean ~ gdppc_growth + LAGlatent + LAG2latent
                  + v2mecenefm 
                  + v2x_polyarchy #+ cnts_domestic6
                  + logPOP + logGDPpc + v2x_corr, data=subset) # controls
summary(ldv_lag2, vcov=vcovBK)

stargazer(ldvBASE, ldv_demo_inter, ldv_media_inter, ldv_lag2)

# (0) baseline LDV 
ldvBASE <- dyn$lm(latentmean ~ gdppc_growth + LAGlatent + v2mecenefm 
                  + v2x_polyarchy #+ cnts_domestic6
                  + logPOP + logGDPpc + v2x_corr, data=subset) # controls
summary(ldvBASE, vcov=vcovBK)

BaselineLDV_residuals <- ldvBASE$residuals
acf(BaselineLDV_residuals) # include more lags


# (1) LDV + intercation (polyarchy)
ldv_demo_inter <- dyn$lm(latentmean ~ gdppc_growth*v2mecenefm + LAGlatent +
                    v2x_polyarchy + v2x_corr +
                    + cnts_domestic6 + logPOP + logGDPpc, data=subset)
summary(ldv_demo_inter)
# =>  do not include

# (1.2) LDV + intercation (media)
ldv_media_inter <- dyn$lm(latentmean ~ gdppc_growth*v2x_polyarchy + LAGlatent +
                    v2x_corr + v2mecenefm +
                    + cnts_domestic6 + logPOP + logGDPpc, data=subset)
summary(ldv_media_inter)

#########################
#########################
# (2) ADL: lagged econ growth
# not good
adl_growth <- dyn$lm(latentmean ~ gdppc_growth + LAGlatent + LAGgrowth + 
                       v2mecenefm + v2x_polyarchy + v2x_corr +
                       cnts_domestic6 + logPOP + logGDPpc, data=subset)
summary(adl_growth, adl_repr)
# no lag's influence 
stargazer(adl_growth, adl_repr, adl_latent_2growth, adl_inter)


# (3) ADL: lagged repressions
# good
adl_repr <- dyn$lm(latentmean ~ gdppc_growth + LAGlatent + LAG2latent +
                      v2x_polyarchy + v2x_corr +
                      v2mecenefm + v2x_polyarchy +
                      logPOP + logGDPpc, data=subset)
summary(adl_repr)
acf(adl_repr$residuals)


# (4) ADL: lagged econ growth + lagged2 repr
# good
adl_latent_2growth <- dyn$lm(latentmean ~ gdppc_growth + LAGlatent + LAG2latent + LAGgrowth + v2mecenefm + 
                       v2x_polyarchy + v2x_corr +
                       logPOP + logGDPpc, data=subset)
summary(adl_latent_2growth)
acf(adl_latent_2growth$residuals)

#(5) interaction

adl_inter <- dyn$lm(latentmean ~ gdppc_growth*v2x_polyarchy + LAGlatent + LAG2latent +
                      v2x_polyarchy + v2x_corr +
                      v2mecenefm +
                      logPOP + logGDPpc, data=subset)
summary(adl_inter)

######################
# best model without media: elect demo is signif
adl_no_media <- dyn$lm(latentmean ~ gdppc_growth + LAGlatent + LAGgrowth + 
    LAG2latent + cnts_domestic6 + v2x_corr +
      v2x_polyarchy + logPOP + logGDPpc, data = subset)
summary(adl_no_media)

# best model without media, corr: elect demo is signif
adl_no_media_corr <- dyn$lm(latentmean ~ gdppc_growth + LAGlatent + LAGgrowth + 
    LAG2latent + cnts_domestic6 + 
      v2x_polyarchy + logPOP + logGDPpc, data = subset)
summary(adl_no_media_corr)

adl_no_media_corr_inter <- dyn$lm(latentmean ~ gdppc_growth + v2x_polyarchy + LAGlatent + LAGgrowth + 
    LAG2latent +  
    logPOP + logGDPpc, data = subset)
summary(adl_no_media_corr_inter)


######################
# fixed effects
adl_fe <- dyn$lm(latentmean ~ gdppc_growth + LAGlatent + LAGgrowth + 
    LAG2latent + v2mecenefm + v2x_polyarchy + v2x_corr + 
      cnts_domestic6 + as.factor(COWc) +
    logPOP + logGDPpc, data = subset)
```


Compare the model and upload the results. 
```{r}
# compare different LDV+riots, LDV+riots+more controls

# 6 models
# LDV simple. (ldv_riots)
# ADL: lagged econ growth (adl_growth)
# ADL: lagged riots (adl_riots)
# ADL: lagged all (adl_all)

# LDV: 2 lagged repression
# LDV + more controls (ldv_riots_control)

stargazer(ldvBASE, ldv_media_inter, adl_media, title="Compare specifications for media")

stargazer(ldvBASE, adl_growth, adl_3latent, adl_latent_2growth, title="Compare ADL models with the base LDV")

stargazer(subset, title = "Data variables summary")
```


For adl we do not need gmm estimator (limits ols estimator), since glm обощает все instrumental variables. 


Informational criteria:
Given a set of candidate models for the data, the preferred model is the one with the minimum AIC value. Thus, AIC rewards goodness of fit (as assessed by the likelihood function), but it also includes a penalty that is an increasing function of the number of estimated parameters. The penalty discourages overfitting, because increasing the number of parameters in the model almost always improves the goodness of the fit.
```{r}
# ACI informational criteria
AIC(ldvBASE)
AIC(ldv_media_inter)
AIC(adl_media)
AIC(adl_growth)
AIC(adl_3latent) # the best = no autocorrelation
AIC(adl_latent_2growth) # the second best

# all together
AIC(adl_latent_2growth, adl_3latent, adl_growth, adl_media, ldv_media_inter, ldvBASE)



# BIC
BIC(adl_latent_2growth, adl_3latent, adl_growth, adl_media, ldv_media_inter, ldvBASE)
```




```{r}
# subset for autocracies
autocracies <- subset[which(subset$v2x_polyarchy <= 0.5), ]

adl_3latent_auto <- dyn$lm(latentmean ~ gdppc_growth + LAGlatent + LAGgrowth + 
    LAG2latent + v2mecenefm +
      v2x_polyarchy + v2x_corr +
      cnts_domestic6 + logPOP + logGDPpc, data = subset)
summary(adl_3latent_auto)
```


